{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-01 bmvc_review.tex

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large or small($\leq0.5$, or $\geq2$).}
\label{Workflow_figure_EnKCF}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they use
the MOSSE tracker to estimate a target's translation. The scale is
updated in a way where the confidence map is used to determine the
scale change between successive frames. This is because they assume
the scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a
KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation in a highly efficient
manner.  In this paper, we use an ensemble of KCFs in turn, instead of
running them all together on every frame. By doing so, we could still
address the scale change and estimate target's motion efficiently
while increasing run-time performance. In particular, we deploy three
KCF in turn: \textit{target}+\textit{small background} translation
filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Figure \ref{fig:Filters} shows examples of the ROIs
associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
\begin{comment}
{\it We may not need this.}
The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
\end{comment}

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while preserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflow_figure_EnKCF}. The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
  datasets.

\item \textbf{Slight Modification of the proposed {\it E}nKCF for
  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
  the flexibility of the ensemble of KCFs approach we propose. The
  original {\it E}nKCF is slighlty modified to track in low frame rate
  videos ($10$fps) dominated by large ego-motion. We do not integrate
  the particle filter in {\it E}nKCF2 as we test it on a temporally
  downsampled UAV123 dataset (UAV123$\_$10fps) including sequences
  with large ego-motion on a UAV platform. Particle Filter can be
  deployed in case the camera motion is known. The run-time
  performance decreases to $150$ fps, however, ratio of the video
  frame rate and run-time performance is similar to {\it E}nKCF. The
  proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.

@@

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%---------------------------------------------------------------------- 
\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
\label{Workflow_figure_EnKCF}
\end{figure*}

\begin{figure*}[!t]
\centering
\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
\label{Workflow_figure_EnKCF2}
\end{figure*}

In this paper, we extend the KCF in that multiple KCFs are deployed,
in turn, to address a target's scale change and dynamic maneuvers
while preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of KCF computation results in a
small-footprint, executable. Such a fast execution will facilitate to
deploy the proposed algorithm on any embedded systems.

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Figure \ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
elementwise multiplication, resulting in a scale estimation in a
higher speed.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

>>>>

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large ($\leq0.5$, or $\geq2$).}
\label{ResultsIntroduction}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they use
the MOSSE tracker to estimate a target's translation. The scale is
updated in a way where the confidence map is used to determine the
scale change between successive frames. This is because they assume
the scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a
KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation in a highly efficient
manner.  In this paper, we use an ensemble of KCFs in turn, instead of
running them all together on every frame. By doing so, we could still
address the scale change and estimate target's motion efficiently
while increasing run-time performance. In particular, we deploy three
KCF in turn: \textit{target}+\textit{small background} translation
filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Fig.~\ref{fig:Filters} shows examples of the ROIs
associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
\begin{comment}
{\it We may not need this.}
The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
\end{comment}

\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
(a) \\
\bmvaHangBox{\includegraphics[width=10.0cm]{./figures/Workflow_EnKCF2+PF.pdf}}\\
(b)
\end{tabular}
\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker (a). It is slightly modified to handle extreme ego-motion
and we call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
\label{Workflows}
\end{figure}
The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while preserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflows}. The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
  datasets.

\item \textbf{Slight Modification of the proposed {\it E}nKCF for
  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
  the flexibility of the ensemble of KCFs approach we propose. The
  original {\it E}nKCF is slighlty modified to track in low frame rate
  videos ($10$fps) dominated by large ego-motion. We do not integrate
  the particle filter in {\it E}nKCF2 as we test it on a temporally
  downsampled UAV123 dataset (UAV123$\_$10fps) including sequences
  with large ego-motion on a UAV platform. Particle Filter can be
  deployed in case the camera motion is known. The run-time
  performance decreases to $150$ fps, however, ratio of the video
  frame rate and run-time performance is similar to {\it E}nKCF. The
  proposed framework can be seen in fig.~\ref{Workflows}.
%\begin{figure*}[!t]
%\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
%\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
%\label{Workflow_figure_EnKCF}
%\end{figure*}
%\begin{figure*}[!h]
%\centering
%\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
%\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
%\label{Workflow_figure_EnKCF2}
%\end{figure*}

@@

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%---------------------------------------------------------------------- 
In this paper, we extend the KCF in that multiple KCFs are deployed,
in turn, to address a target's scale change and dynamic maneuvers
while preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of KCF computation results in a
small-footprint, executable. Such a fast execution will facilitate to
deploy the proposed algorithm on any embedded systems.

The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background twice bigger than that of the first filter, $R_{t}^{S}$,
\textit{target}+\textit{large background}. We set up {\it E}nKCF in
this way because we believe a correlation filter for learning a
target's translation should include its background to better
discriminate the target from its background and another correlation
filter is prepared to focus on the target itself to estimate the right
size or scale of the target. Fig.~\ref{fig:Filters} shows examples
of the region of interest (ROI) covered by each of three filters. We
believe that a filter for learning a target's translation should
include its background. In addition, making the ROI for the scale
filter, $R_{s}$, tighter reduces the size of the template for the
elementwise multiplication, resulting in a scale estimation in a
higher speed.
\begin{figure}[!h]
\centering
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
\caption{The video frame and the learned scale correlation filters are shown next to it. 
The models in the top row correspond to the scale filter trained every frame whereas the bottom row shows the scale filter updated every $5$ frames. 
Filters updated every five frame and every frame display very large correlation.}
\label{fig:Filters_Comparison}
\end{figure}
